%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ACM ICPC 2016-2017, NEERC                                      %
% Northern Subregional Contest                                   %
% St Petersburg, October 22, 2016                                %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Problem F. Folding                                             %
%                                                                %
% Original idea         Georgiy Korneev                          %
% Problem statement     Georgiy Korneev                          %
% Test set              Georgiy Korneev                          %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Problem statement                                              %
%                                                                %
% Author                Georgiy Korneev                          %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{problem}{Folding}{folding.in}{folding.out}{\timeLimit}

% Original idea : Georgiy Korneev
% Text          : Georgiy Korneev
% Tests         : Georgiy Korneev

As you can remember, Alex is fond of origami. She switched from squares
to rectangles, and rectangles are much more difficult to master.
Her main interest is to determine what is the minimum possible number of
folds required to transform $W \times H$ rectangle to $w \times h$ one.
The result of each fold should also be rectangular, so it is only allowed to
make folds that are parallel to the sides of the rectangle.

Help Alex and write a program that determines the minimum required number of folds.

\InputFile

The first line of the input contains two integers $W$ and $H$~---
the initial rectangle dimensions.  
The second line contains two more integers $w$ and $h$~---
the target rectangle dimensions ($1 \le W, H, w, h \le 10^9$).

\OutputFile

Output a single integer~--- the minimum required number of folds
to transform the initial rectangle to the target one.

If the required transformation is not possible, output $-1$.

\Examples

\begin{example}
\exmp{
2 7
2 2
}{
2
}%
\exmp{
10 6
4 8
}{
2
}%
\exmp{
5 5
1 6
}{
-1
}%
\end{example}

In the first example you should fold $2\times7$ rectangle to $2\times4$, 
and then to $2\times2$.

In the second example you should fold $10\times6$ rectangle to $10\times4$, 
then to $8\times4$, and rotate it to $4\times8$.

In the third example it is impossible to fold $5\times5$ rectangle to $1\times6$ one
(remember that folds must be parallel to the rectangle sides).

\end{problem}

